Practical Optional Types for Clojure

### 2015-06-15 formal-model.tex
add T-New, T-Method
remove resolve functions.
Use Mth/Ctor/Fld in T-{Method,New,Field}.
TODO TJ metafunction
updating proof
finish BetaMulti proof
update metatheory

We formalize our type system following~\citet{TF10}
(with differences highlighted in $\trdiff{\text{blue}}$).
The typing judgment 
$$
{\judgement   {\propenv}
              {\e{}} {\t{}}
  {\filterset {\thenprop {\prop{}}}
              {\elseprop {\prop{}}}}
  {\object{}}}
$$
says expression \e{} is of type \t{} in the 
proposition environment $\propenv{}$, with 
`then' proposition {\thenprop {\prop{}}}, `else' proposition {\elseprop {\prop{}}}
and object \object{}. We write 
{\judgementtwo{\propenv}{\e{}} {\t{}} if we are only interested in the type.

@@

\begin{figure*}
  \footnotesize
  \begin{mathpar}
    %{\TDo}
    %{\TClass}
    %{\TIf}
    {\TAbs}
    \begin{array}{c}
      {\TSubsume}\\\\
      {\TNum}
    \end{array}
    \begin{array}{c}
      {\TConst}\\\\
      {\TKw}\\\\
      {\TClass}
    \end{array}
    \begin{array}{c}
      {\TTrue}\\\\
      {\TFalse}\\\\
      {\TNil}
    \end{array}

@@

    \classtableallsyntax{}
  \end{altgrammar}
  $$
  \begin{mathpar}
    {\TNewStatic}

    {\TMethodStatic}

    %{\TInstance}
  \end{mathpar}
 \classtablelookupsyntax{}
 \begin{mathpar}
  \begin{altgrammar}
    \convertjavatypenil{}
  \end{altgrammar}
  \begin{altgrammar}
    \convertjavatypenonnil{}
  \end{altgrammar}
\end{mathpar}
  \begin{mathpar}
    \BField{}

@@

\begin{mathpar}
    {\TFieldStatic}
\end{mathpar}

>>>>

We formalize our type system following~\citet{TF10}
(with differences highlighted in $\trdiff{\text{blue}}$).
The typing judgment 
$$
{\judgementrewrite   {\propenv}
              {\e{}} {\t{}}
  {\filterset {\thenprop {\prop{}}}
              {\elseprop {\prop{}}}}
  {\object{}}
  {\ep{}}}
$$
says expression \e{} is of type \t{} in the 
proposition environment $\propenv{}$, with 
`then' proposition {\thenprop {\prop{}}}, `else' proposition {\elseprop {\prop{}}}
and object \object{}, and rewrites to \ep{}. We write 
{\judgementtworewrite{\propenv}{\e{}} {\t{}}{\ep{}} if we are only interested in the type
  or
{\judgement   {\propenv}
              {\e{}} {\t{}}
  {\filterset {\thenprop {\prop{}}}
              {\elseprop {\prop{}}}}
  {\object{}}}
for expressions that rewrite to itself.

@@

\begin{figure*}
  \footnotesize
%   \judgbox{
%{\judgementrewrite   {\propenv}
%              {\e{}} {\t{}}
%  {\filterset {\thenprop {\prop{}}}
%              {\elseprop {\prop{}}}}
%  {\object{}}{\ep{}}}}
%           {Under proposition environment $\propenv{}$, 
%             expression \e{} is of type \t{}
%             with  \\
%
%`then' proposition {\thenprop {\prop{}}}, `else' proposition {\elseprop {\prop{}}}
%and object \object{} and rewrites to \ep{}.}
  \begin{mathpar}
    %{\TDo}
    %{\TClass}
    %{\TIf}
    {\TAbs}
    \begin{array}{c}
      {\TSubsume}\\\\
      {\TNum}
    \end{array}
    \begin{array}{c}
      {\TConst}\\\\
      {\TKw}\\\\
      {\TClass}
    \end{array}
    \begin{array}{c}
      {\TTrue}\\\\
      {\TFalse}\\\\
      {\TNil}
    \end{array}

@@

    \classtableallsyntax{}
  \end{altgrammar}
  $$
  \begin{mathpar}
    {\TNew}

    {\TMethod}

    %{\TInstance}
  \end{mathpar}
 %\classtablelookupsyntax{}
 \begin{mathpar}
  \begin{altgrammar}
    \convertjavatypenil{}
  \end{altgrammar}
  \begin{altgrammar}
    \convertjavatypenonnil{}
  \end{altgrammar}
  \\
  \begin{altgrammar}
    \converttctype{}
  \end{altgrammar}
\end{mathpar}
  \begin{mathpar}
    \BField{}

@@

\begin{mathpar}
    {\TField}
\end{mathpar}
